\thetitle

### 2021-03-03 writing/sample.tex
adding total mutant and scenrio numbers in section 7

To make the experiment computationally feasible and statistically precise,
stratified uniform random sampling with three levels of stratification becomes
necessary.  The first two levels group mutants first by benchmark and then by
mutator.  The set of randomly select from the mutants of each benchmark is
checked to make sure that, per benchmark, the sample reflects the diversity of
mutants with respect to the mutators that generated them.  Specifically, the
process samples 80 mutants with interesting scenarios per benchmark,
evenly-distributed across all of the mutators that contribute mutants for the
benchmark.  At the third level, the sampling process draws 96 random interesting
scenarios from each configuration lattice with replacement.

%% This looks like a repeat of the above, made concrete for the benchmark set

% In summary, the sampling process takes advantage of ancillary information to
% deliver a sufficiently large representative set of scenarios.  Concretely, we
% test each mode of the rational programmer on 72,192 randomly selected
% interesting debugging scenarios spread across both benchmarks and mutators.
% Furthermore, stratified random sampling allows us to derive precise conclusions
% about the proportion of the whole population that satisfies a given trait from
% the sample despite the population's heterogeneity.  That property is exactly
% what we need to project comparisons about the usefulness of various modes of the
% rational programmer from the sample to the set of all interesting debugging
% scenarios.

%% we use the following algorithm to select the 80 mutants evenly distributed across all of the mutators that do produce mutants of a benchmark:
%% 1. Treat each mutator as a bucket containing the mutants produced by that mutator
%% 2. Let the target-sample-size be 80
%% 3. Let the bucket-sample-size be target-sample-size/number-of-buckets
%% 4. For each bucket, do
%%    1. Randomly remove min(bucket-sample-size, mutants-in(bucket)) mutants from the bucket
%%    2. Set target-sample-size = target-sample-size - (the number of mutants removed)
%% 5. If target-sample-size is empty, done; else, go back to 3.

>>>>

To make the experiment computationally feasible and statistically sound,
stratified uniform random sampling with three levels of stratification becomes
necessary.  The first two levels group mutants first by benchmark and then by
mutator.  The set of the randomly selected mutants of each benchmark is
checked to make sure that, per benchmark, the sample reflects the diversity of
mutants with respect to the mutators that generated them.  Specifically, the
process samples 80 mutants with interesting scenarios per benchmark,
evenly-distributed across all of the mutators that contribute mutants for the
benchmark. Some benchmarks has less than  80 mutants with interesting scenarios
in which case the process collects them all which results in a total of 756 mutants
across all benchmarks.  
At the third level, the sampling process draws 96 random interesting
scenarios from each configuration lattice with replacement. In sum, the
final sample consists of 72,200 interesting scenarios.
